%-------------------------------------------------------------------------------
%   WORK EXPERIENCE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

\begin{cventries}

  \cventry
  {Lead Engineer}
  {Mozayedegar}
  {Tabriz, Iran}
  {Jul 2022 – Present}
  {
    \begin{cvitems}
      \item {Led architecture and development of an online auction platform serving \textbf{100K+ registered users} using \textbf{.NET, Next.js, React Native}.}
      \item {Designed a high-availability infrastructure with cluster replication, DB replication, MinIO replication, and PITR backups.}
      \item {Implemented GitLab-based CI/CD delivering \textbf{10+ daily staging deployments} and weekly production releases.}
      \item {Set up full-stack logging/monitoring: \textbf{Grafana/Prometheus} (infra) and \textbf{ELK stack} (app), significantly reducing debugging time and user-facing errors.}
      \item {Built internal tooling: linting rules, reusable components, and private npm/NuGet packages reducing new project setup time by ~60\%.}
      \item {Trained and mentored \textbf{~10 engineering interns} through 3–6 month programs, most of whom were hired full-time.}
      \item {Performed multiple architectural migrations as load increased to maintain consistent performance and reliability.}
      \item {Architected a production AI-powered pipeline that automatically reads daily newspapers, detects tender/auction sections using custom vision models, performs OCR, and formats content using LLMs for ingestion into the main auction platform.}
      \item {Designed and led implementation of a scraping + LLM normalization pipeline for government tender websites.}
      \item {Led \textbf{2 AI engineers} who implemented Python-based AI services following the end-to-end pipeline architecture and blueprint I provided.}    \end{cvitems}
  }


%---------------------------------------------------------

  \cventry
    {Senior Software Engineer (Contract)}
    {Multiple Clients — Leal Technologies, Synaps AI, theCodeBase, CoverMe}
    {Remote}
    {2022 – 2025}
    {
      \begin{cvitems}
        \item {\textbf{Built two full-stack products from scratch} (Thawapp, Glim) for a startup studio using TypeScript-first stacks. Delivered production-quality MVPs under tight timelines.}
        \item {Thawapp: \textbf{PostgreSQL, tRPC, Next.js, TailwindCSS, shadcn, Expo, React Native Reusable}, SST. Built a shared UI/component system improving code reuse across platforms.}
        \item {Glim: \textbf{DynamoDB, SST, Next.js, tRPC}. Integrated Google OAuth/Gmail APIs and achieved \textbf{OWASP-compliant verification}.}
        \item {Architected and developed the entire \textbf{AI recruiting automation platform} for Synaps AI, enabling AI-generated and AI-scored text, video, and code interviews.}
        \item {Scaled the platform to \textbf{50+ enterprise clients} and supported \textbf{1K AI-evaluated interviews} in a single batch for a major Turkish company.}
        \item {Reduced DynamoDB query latency and cost by introducing optimized \textbf{GSIs}.}
        \item {Led 3 engineers and established engineering processes, coding standards, and architecture guidelines.}
        \item {Contributed to a large multi-team ecosystem with \textbf{11 microservices} powering a dual-sided C2C + vendor e-commerce platform.}
        \item {Improved service architecture using \textbf{Clean Architecture}, shared NuGet libraries, and standardized error-handling (ErrorOrSuccess).}
        \item {Designed and integrated shipping workflows with multiple Turkish postal providers.}
        \item {Redesigned a hospital-facing SaaS product (CoverMe), modernizing the frontend using \textbf{React Hook Form + TypeScript}. Reduced runtime errors by \textbf{~40\%} and form failures by \textbf{~30\%}.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Senior Software Engineer}
    {Roombadi}
    {Istanbul, Turkey | Remote}
    {Sep 2021 – Sep 2023}
    {
      \begin{cvitems}
        \item {Led development of a roommate matching platform using \textbf{React Native, Next.js, .NET}, achieving \textbf{1,000+ DAU}.}
        \item {Built a serverless backend using \textbf{AWS Lambda, API Gateway, DynamoDB}, achieving \textbf{60\% cost reduction}.}
        \item {Optimized system performance to maintain \textbf{<300ms latency} using Redis and Elasticsearch.}
        \item {Implemented a testing suite (Jest, RTL, Cypress) reaching \textbf{98\% coverage}, ensuring reliable releases.}
        \item {Improved SEO via SSR (Next.js), increasing organic traffic by \textbf{20\%}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer}
    {Sobh Parlar Asia}
    {Tabriz, Iran}
    {Oct 2018 – Sep 2021}
    {
      \begin{cvitems}
        \item {Developed a centralized Smart Home IoT platform using \textbf{.NET, Next.js, React Native}.}
        \item {Handled \textbf{10K MQTT events per minute} across multi-device households (avg. 4 devices per user).}
        \item {Built reusable UI components and frontend architecture improving development efficiency.}
        \item {Implemented robust security measures preventing SQL Injection, XSS, and personal data leaks.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}